---
output: github_document
---

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/simulacr)](https://cran.r-project.org/package=simulacr)

# Welcome to the *simulacr* package!

This package is under development. Do not use it without contacting the authors first.

## Installing the package

To install the current stable, CRAN version of the package, type:
```{r install, eval = FALSE}
install.packages("simulacr")
```

To benefit from the latest features and bug fixes, install the development, *github* version of the package using:
```{r install2, eval = FALSE}
devtools::install_github("reconhub/simulacr")
```

Note that this requires the package *devtools* installed.


# What does it do?

*simulacr* implements outbreak simulation using branching processes. The main
features of the package include:

* `simulate_outbreak`: the main function, allowing to simulate outbreaks for
  specified values of reproduction number, incubation period, duration of
  infectiousness, and optionally reporting delays; it outputs a linelist stored
  as a `data.frame` with the class `outbreak`, including information on
  transmission chains; the output can be converted to `epicontacts` objects for
  visualisation, and plotted using `plot(...)`
  
* `as_epicontacts`: a function to convert `outbreak` object to `epicontact`;
  called implicitely when plotting `outbreak` objects
  
* `make_disc_gamma`: wrapper function to build discretised Gamma distributions
  easily
  
* `draw_labels`: wrapper function to generate random alphanumeric labels

<br>




# Example

This brief example illustrates how we can simulate an outbreak, with different
ways of specifying input distributions.

## Specifying delay distributions

Distributions can be specified in different ways:

* as a discretised distribution stored as `distcrete` object, e.g. generated via
  `make_disc_gamma`
* as a function with a single argument (the delay) computing probability mass
  function (pmf) of different delays
* as a vector of $n$ positive numbers, taken to be the pmf of delays of
  0:($n$-1)
  
We illustrate these different options below, with:

* a flat distribution of the incubation time 1-4 days (all other values have a
null probability)
* an infectious period defined as a discretised Gamma distribution stored as a
  `distcrete` object
* a reporting delay following a Poisson distribution, specified as a function

```{r distributions}
library("simulacr")

incubation <- c(0, 1, 1, 1, 1) # numbers = unscaled PMF
infectious_period <- make_disc_gamma(10, 7) # distcrete object
reporting <- function(x) dpois(x, 5) # PMF function

```

## Running simulations

```{r simulations}
set.seed(1)
x <- simulate_outbreak(R = runif(100, 1, 3), # random values on [1;3]
                       dist_incubation= incubation,
                       dist_infectious_period = infectious_period,
                       dist_reporting = reporting)

```

The output is a `data.frame` with the class `outbreak`, which contains a
linelist of cases:

```{r view_x}

class(x)
dim(x)
head(x)
tail(x)

```

This object can be plotted using (this will open an interactive graph:

```{r plot_x}

plot(x)
  

```

For any work relying on transmission trees, it may be easiest to convert the
`outbreak` object to an `epicontacts`:

```{r convert_x}
net <- as_epicontacts(x)
net
```





# Resources

## Vignettes

No vignette currently available.


## Getting help online

Bug reports and feature requests should be posted on *github* using the [*issue*](http://github.com/reconhub/simulacr/issues) system. All other questions should be posted on the **RECON forum**: <br>
[http://www.repidemicsconsortium.org/forum/](http://www.repidemicsconsortium.org/forum/)

Contributions are welcome via **pull requests**.

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

